\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Evan}{Hirsh}{ \urlstyle{same}\href{https://github.com/evanextreme}{github.com/evanextreme} | \href{https://www.linkedin.com/in/evanhirsh/}{linkedin.com/in/evanhirsh/} | \href{mailto:evan@ehirsh.com}{evan@ehirsh.com}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.49\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     WORK EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Work Experience}
\runsubsection{Nextly}
\descript{| Business Strategist }
\location{Jul 2019 - Present | São Paulo, SP, Brazil}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Focused on strategies to allow the company expansion to overseas territories such as the US, Canada, and Europe.
\item Developed new internal procedures and improved existing ones to maximize sales results.
\item Supervised development teams to ensure the software quality required by the partners.
\end{tightemize}
\sectionsep

\runsubsection{Nerit}
\descript{| Frontend Developer }
\location{Sep 2017 – Nov 2017 | Belo Horizonte, MG, Brazil}
\begin{tightemize}
\item Responsible for the development of websites based on the company customer's needs.
\item Maintained and improved proprietary software used internally by the company.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{PUC Minas}
\descript{Bachelor in Computer Science}
\location{Dec 2021 | Belo Horizonte, MG, Brazil}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Technical Skills}
\location{Proficient with}
JavaScript \textbullet{} TypeScript \textbullet{} Node.js \textbullet{} Express.js \\
React \textbullet{} Redux \textbullet{} Python \textbullet{} C \textbullet{} C++ \textbullet{} Solidity \\ ERC-20 \textbullet{} Git \textbullet{} MongoDB \textbullet{} Postgres \textbullet{} MySQL \\ HTML5 \textbullet{} CSS3 \textbullet{} AWS \textbullet{} Heroku \textbullet{} Netlify \textbullet{} Agile Development \textbullet{} Linux \textbullet{} Arduino \textbullet{} TDD \textbullet{} Circuit\\Prototyping \\
\location{Familiar with:}
C\# \textbullet{} PHP \textbullet{} Java \textbullet{} Native Android Development \\ Docker \textbullet{} Assembly \textbullet{} Raspberry Pi
\sectionsep

\subsection{Soft Skills}
\location{Strong}
Leadership \textbullet{} Resourcefulness \textbullet{} Grit \textbullet{} Public Speaking \\
Stock Investing \textbullet{} Cryptocurrency Investing
\sectionsep

\section{Languages}
\subsection{Proficiency Level}
\location{Native proficiency:}
Portuguese \textbullet{} English \\
\location{Working proficiency:}
Spanish

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.5\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    ENTREPRENEURIAL EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Entrepreneurial Experience}

\runsubsection{Cryptic Activist}
\descript{| Founder \& CEO}
\location{Oct 2019 – Present}
\descript{Under development}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item An online platform for publishing blog posts and articles by the community, weekly podcast episodes, and online courses primarily focused on blockchain development, blockchain real-life applications, cypherpunk and libertarian topics.
\end{tightemize}
\location{Technologies used: MongoDB, Express.js, React, Redux, Node.js, Solidity, ERC-20, Pyhthon, C++} 
\sectionsep

\runsubsection{Canada Cannabyss}
\descript{| Co-founder \& CTO }
\location{May 2019 - Present | Victoria, BC, Canada}
\descript{Current monthly revenue: C\$ 7.000/month}
\begin{tightemize}
\item Developed the identity of the Canada Cannabyss brand.
\item Create internal procedures and workflows to maximize development outcomes. 
\item Launched the brand in the market during the early-stage cannabis legalization in Canada.
\item Developed all software used at Canada Cannabyss such as resource and sales management, data visualization and security.
\end{tightemize}
\location{Technologies used: Python, Django, TensorFlow, matplotlib, Postgres} 
\sectionsep


\runsubsection{Canada E-Cigs}
\descript{| Co-owner \& CTO }
\location{Jan 2019 – Present | Edmonton, AB, Canada}
\descript{Current monthly revenue: C\$ 8.000/month}
\begin{tightemize}
\item Responsible for the development, supervision and maintenance of the entire Canada E-Cigs eCommerce Python-based ecosystem.
\item Developed alternative marketing and SEO strategies based on the limitations due to the e-cigarettes marketing regulations. 
\item Implemented strong Python-based technologies for data visualization, to better understand all the data generated by the company to enhance future business decisions
\end{tightemize}
\location{Technologies used: Python, Django, TensorFlow, matplotlib, Postgres} 
\sectionsep

\runsubsection{Braw}
\descript{| Co-founder \& CTO }
\location{Nov 2017 – Present | Belo Horizonte, MG, Brazil}
\descript{Current monthly revenue: R\$ 25.000/month}
\begin{tightemize}
\item In charge of the software development for an innovative straw cigarettes mass production machine..
\item Accountable for the marketing strategies development for the national market.
\end{tightemize}
\location{Technologies used: C, Python} 
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
